% What's the problem?
% Why is it a problem? Research gap left by other approaches?
% Why is it important? Why care?
% What's the approach? How to solve the problem?
% What's the findings? How was it evaluated, what are the results, limitations, 
% what remains to be done?

We have many simple tasks that take up our time.
In many (most or all?) cases that is a waste of our time, since these tasks 
could be performed autonomously by computers.
Here we cover some aspects of such tasks and how we successfully automate them.
We cover some aspects of the following topics:
\begin{itemize}
  \item automated grading,
  \item automatically report results to LADOK,
  \item finding results of late students, and
  \item managing TAs.
\end{itemize}

\endinput

In terms of grading we cover the following aspects:
\begin{itemize}
  \item \alert<2>{Reporting to Canvas when connected to automated grading (\eg 
    gits-15, Kattis, mail, zoom participation \etc)}
  \item \alert<2>{Grading/commenting assignments}
\end{itemize}

  \begin{example}[Reporting]
    \begin{itemize}
      \item \alert<2>{Bulk reporting}
      \item \alert<2>{Formulas for grading}
      \item \alert<2>{Canvas to LADOK with correct dates}
      \item \alert<2>{Automated grading + reporting}
    \end{itemize}
  \end{example}

\begin{frame}[fragile]\label<2>{WishLateStudents}
  \begin{example}[Late students]
    \begin{itemize}
      \item \alert<2>{Discover finished course or components}
      \item \alert<2>{Grade students from different course rounds}\footnote{%
          More difficult with locked Canvas rooms.
        }:
        \begin{description}
          \item[Scenario 1] \alert<2>{Get email from student who claims they've 
            finished but can't see any result in LADOK.}

          \item[Scenario 2] The student took the exam during another round than 
            what they originally registered for.
        \end{description}

      \item \alert<2>{It's more work to track students from previous rounds, 
        what they've finished, bonus points etc.}
    \end{itemize}
  \end{example}
\end{frame}

\begin{frame}[fragile]
  \begin{example}[Managing students]
    \begin{itemize}
      \item Time booking
      \item Group formation
      \item Manage course related emails or Canvas messages
      \item Manage discussion threads
    \end{itemize}
  \end{example}

  \pause

  \begin{remark}
    \begin{itemize}
      \item Won't cover any of these topics.
      \item But if you want to talk about it, contact us.
    \end{itemize}
  \end{remark}
\end{frame}

\begin{frame}[fragile]\label<2>{WishTA}
  \begin{example}[Managing TAs]
    \begin{itemize}
      \item \alert<2>{Time booking}

      \item \alert<2>{Find potential TAs, the TA pool}
        \begin{itemize}
          \item the TA pool doesn't contain details of which course an 
            individual is suitable to work on.
        \end{itemize}

      \item \alert<2>{Remove students who graduated from the TA pool.}
    \end{itemize}
  \end{example}
\end{frame}

