% What's the problem?
% Why is it a problem? Research gap left by other approaches?
% Why is it important? Why care?
% What's the approach? How to solve the problem?
% What's the findings? How was it evaluated, what are the results, limitations, 
% what remains to be done?

\begin{frame}[fragile]
  \begin{block}{The problem}
    \begin{description}
      \item<+>[What's the problem?] Simple tasks that take up our time.
      \item<+>[Why is it a problem?] We waste time that can be used better.
      \item<+>[What's the approach?] Let a computer do these things instead.
      \item<+>[What are the findings?] This works very well.
    \end{description}
  \end{block}
\end{frame}

We cover some aspects.

\begin{frame}[fragile]\label<2>{WishGradingReporting}
  \begin{example}[Grading]
    \begin{itemize}
      \item Grade/comment assignments when there are several teachers
      \item \alert<2>{Reporting to Canvas when connected to automated grading 
        (\eg gits-15, kattis, mail, zoom participation \etc)}
      \item Grading rubrics (betygsmatriser)
      \item \alert<2>{Grading/commenting assignments}
    \end{itemize}
  \end{example}

  \begin{example}[Reporting]
    \begin{itemize}
      \item \alert<2>{Bulk reporting}
      \item \alert<2>{Formulas for grading}
      \item \alert<2>{Canvas to LADOK with correct dates}
      \item \alert<2>{Automated grading + reporting}
    \end{itemize}
  \end{example}
\end{frame}

\begin{frame}[fragile]\label<2>{WishLateStudents}
  \begin{example}[Late students]
    \begin{itemize}
      \item \alert<2>{Discover finished course or components}
      \item \alert<2>{Grade students from different course rounds}\footnote{%
          More difficult with locked Canvas rooms.
        }:
        \begin{description}
          \item[Scenario 1] \alert<2>{Get email from student who claims they've 
            finished but can't see any result in LADOK.}

          \item[Scenario 2] The student took the exam during another round than 
            what they originally registered for.
        \end{description}

      \item \alert<2>{It's more work to track students from previous rounds, 
        what they've finished, bonus points etc.}
    \end{itemize}
  \end{example}
\end{frame}

\begin{frame}[fragile]
  \begin{example}[Managing students]
    \begin{itemize}
      \item Time booking
      \item Group formation
      \item Manage course related emails or Canvas messages
      \item Manage discussion threads
    \end{itemize}
  \end{example}

  \pause

  \begin{remark}
    \begin{itemize}
      \item Won't cover any of these topics.
      \item But if you want to talk about it, contact us.
    \end{itemize}
  \end{remark}
\end{frame}

\begin{frame}[fragile]\label<2>{WishTA}
  \begin{example}[Managing TAs]
    \begin{itemize}
      \item \alert<2>{Time booking}

      \item \alert<2>{Find potential TAs, the TA pool}
        \begin{itemize}
          \item the TA pool doesn't contain details of which course an 
            individual is suitable to work on.
        \end{itemize}

      \item \alert<2>{Remove students who graduated from the TA pool.}
    \end{itemize}
  \end{example}
\end{frame}

